Extended Abstract

### 2021-07-28 paper/paper.tex
Fix remarks regarding Kobayashi and Padovani's work

The \picalc{} \cite{MilnerPW92a,Milner99} models concurrent processing, boiling it down to the transmission of data over communication channels --- where channels too are sent as payload.
The linear \picalc{} \cite{KobayashiPT96} introduces a type system that ensures that every channel is used \emph{exactly} once.
This restriction ensures communication safety and the absence of race conditions.
We generalise to a \picalc{} with linear and shared types, where the input and output capabilities of a channel are either usage $0$ (cannot be used to transmit), usage $1$ (must be used exactly once), or usage $\omega$ (unlimited use).
\footnote{
  Why support a usage $0$ instead of removing the variable from context? it allows the syntax to be independent from the type system, and it allows for a \emph{polarised} treatment of channels, where the same channel variable is used for both input and output.
  }

@@

To the best of our knowledge, this problem has only been treated in Padovani's work on type reconstruction for composite types \cite{Padovani15}.
However, his work does not appear to be mechanised, and metatheoretical properties like soundness and completeness are only informally addressed.
With this work, we aim to:
\begin{itemize}
  \item State and prove clear soundness and completeness theorems for both constraint collection and constraint resolution (\autoref{inference}).
  \item Mechanise in Agda the totality of this work.
\end{itemize}

>>>>

The \picalc{} \cite{MilnerPW92a,Milner99} models concurrent processing, boiling it down to the transmission of data over communication channels --- where channels too are sent as payload.
Type systems for the \picalc{} that support linearity \cite{KobayashiPT96} ensure that linear channels are used \emph{exactly once}, which guarantees communication safety and the absence of race conditions.
We follow this line of work with a \picalc{} with linear and shared types, where the input and output capabilities of a channel are either usage $0$ (cannot be used to transmit), usage $1$ (must be used exactly once), or usage $\omega$ (unlimited use).
\footnote{
  Why support a usage $0$ instead of removing the variable from context altogether? it allows the syntax to be independent from the type system, and moreover for a \emph{polarised} treatment of channels, where the same channel variable is used for both input and output.
  }

@@

To the best of our knowledge, this problem has not yet been mechanised, and has only been treated in Padovani's work on type reconstruction for composite types \cite{Padovani15}.
With this work, we aim to:
\begin{itemize}
  \item State and prove clear soundness and completeness theorems for both constraint collection and constraint resolution (\autoref{inference}).
  \item Mechanise in Agda the totality of this work.
\end{itemize}
